``Interestingness'' in Mathematical Theory Exploration

### 2019-10-23 PhDThesis/bucketing.tex
Adjust scale of graphs
We want the two survival plots in a column next to the two failure lines. This
requires that each graph be at most 50% of the width.

We can set the width (from which the height is calculated via the golden ratio)
in the Python code. The larger this is, the more spread-out the graph contents
are.

We can use a scalebox in LaTeX to grow/shrink the graphs. This doesn't affect
the graph's layout, but it does make the whole thing smaller.

We want the width-proportion (in Python) * scale factor (in LaTeX) to be at most
0.5. This version uses 0.75 in Python and 0.66 in LaTeX

\begin{figure}
  \centering
  \scalebox{0.5}{\input{images/steppedall.pgf}}
  \scalebox{0.5}{\input{images/timeoutsall.pgf}}
  \scalebox{0.5}{\input{images/steppednontoxic.pgf}}
  \scalebox{0.5}{\input{images/timeoutsnontoxic.pgf}}
  \caption{Kaplan-Meier survival plot for running \quickspec{} on inputs
    containing various numbers of definitions, sampled from TIP. The x axis
    denotes running time, which we cut short after 300 seconds. The height of
    each line shows the proportion of \quickspec{} runs which were still going
    at that time (lower is better). First plot is for all TIP definitions,
    second plot removes runs given ``toxic'' definitions.
    \iffalse
    TODO: Alison: The key needs further explanation (either here or in the caption)
    TODO: Alison: Label the y axis (on both)
    \fi}
  \label{fig:survival}
\end{figure}

>>>>

\begin{figure}
  \centering
  \scalebox{0.69}{\input{images/steppedall.pgf}}
  \scalebox{0.69}{\input{images/timeoutsall.pgf}}
  \scalebox{0.69}{\input{images/steppednontoxic.pgf}}
  \scalebox{0.69}{\input{images/timeoutsnontoxic.pgf}}

  % NOTE: The list-of-figures description given as an optional argument to
  % \caption is needed to allow multiple paragraphs without error.
  \caption[Survival plots for \quickspec{} running on different sized
  signatures.]{Running times when using \quickspec{} to explore signatures
    sampled from the Theory Exploration Benchmark, The top row includes all
    sampled signatures, whilst the second row excludes those containing ``toxic''
    definitions.

    \textbf{Left} Kaplan-Meier survival plots for exploring signatures sampled
    from our TEB. Time runs horizontally, which we cut short after 300 seconds.
    Each line tracks a population of signatures of a given size (shown in the
    legend), as they're explored using \quickspec{}. The height of each line
    shows the proportion of processes still running after that amount of time
    (lower is better). Shaded regions denote 95\% confidence intervals.

    \textbf{Right} Proportion of each population which timed out after 300
    seconds, for signatures of different size. This corresponds to a slice
    through the corresponding survival plot at the 300 second mark (if all of
    the measured populations were included). Lines of best-fit use linear
    regression, providing an estimate of the effect that ``toxic'' definitions
    have on failure (timeout) rate.}
    % TODO Put line slopes and error on graph
    % TODO Bottom row should use a second set of samples (chosen to avoid toxic
    % definitions), rather than just filtering down
  \label{fig:survival}
\end{figure}
